Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-02 papers/eccv2018/1_related_work.tex

\paragraph{Pixel-based methods.}
A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}. However, these methods do not scale to terabyte datasets. More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.

@@

>>>>

\paragraph{Pixel-based methods.}
A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally} FIX (superpixels not pixels). However, these methods do not scale to terabyte datasets. More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation,ronneberger2015u} or 3D CNNs~\cite{lee2015recursive,cciccek20163d,turaga2010convolutional}.

@@

Superhuman \cite{lee2017superhuman}
Deep structured learning \cite{funke2017deep}
Multicut brings \cite{beier2017multicut}
DeepEM3D \cite{zeng2017deepem3d}
